MPR case study 2

### 2020-01-24 Code/mrp/Case Study .Rmd
looking into rstanarm

```{r eval = FALSE}
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```

Becasue we are using simulated data we can see how our poststratified predictions compare to the true population

>>>>

```{r eval = FALSE2}
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```

Because we are using simulated data we can see how our poststratified predictions compare to the true population

### 2020-01-24 Code/mrp/mrp-vignette.Rmd
Trying to understand rstanarm
looking into rstanarm

sample <- mrp_sim[["sample"]]
poststrat <- mrp_sim[["poststrat"]]
true_popn <- mrp_sim[["true_popn"]]
```
```{r}
fit <- stan_glmer(
  cat_pref ~ factor(male) + factor(male) * factor(age) + 
    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
  family = binomial(link = "logit"),
  data = sample
)
```

>>>>

sample <- mrp_sim[["sample"]]
poststrat <- mrp_sim[["poststrat"]]
true_popn <- mrp_sim[["true_popn"]]
```

```{r}
sample
```

```{r}
fit <- stan_glmer(
  cat_pref ~ factor(male) + factor(male) * factor(age) + # gender factor and a gender ~ age interaction factor
    (1 | state) + (1 | age) + (1 | eth) + (1 | income), # random intercept with fixed means
  family = binomial(link = "logit"),
  data = sample
)
```

For information on the priors used.
```{r}
prior_summary.stanreg
```
